% arara: lualatex
\documentclass[usearial]{_style/dissertation}

%% Turn off page numbering for the propositions and make the margins on both
%% sides equal and symmetrical.
\geometry{twoside=false}
\pagestyle{empty}

%% Specify the title and author of the thesis. This information will be used on
%% both the English and Dutch side and in the metadata of the final PDF.
\title[Optional Subtitle]{Title}
\author{Albert}{Einstein}

\begin{document}
% Title
\begin{center}

    {\Huge\titlefont\bfseries Propositions}

    \bigskip

    accompanying the dissertation

    \bigskip

    %% Print the title.
    {\makeatletter
        \color{title}
        \titlestyle\bfseries\huge\@title
        \makeatother}

    %% Print the optional subtitle.
    {\makeatletter
        \color{title}
        \ifx\@subtitle\undefined\else
            \large\titlefont\titleshape\@subtitle
        \fi
        \makeatother}

    \bigskip

    by

    \bigskip

    %% Print the full name of the author.
    \makeatletter
    {\large\titlefont\bfseries\@firstnames\ \MakeUppercase{\titleshape\@lastname}}
    \makeatother

\end{center}

\bigskip
\bigskip

\begin{enumerate}

\item If you can't explain it to a six year old, you don't understand it yourself.

\item Anyone who has never made a mistake has never tried anything new.

\item Never memorize something that you can look up.

\item A clever person solves a problem. A wise person avoids it.

\item Reality is merely an illusion, albeit a very persistent one.

\item The world is in greater peril from those who tolerate or encourage evil than from those who actually commit it

\item Concern for man and his fate must always form the chief interest of all technical endeavors.

\item Science can flourish only in an atmosphere of free speech.

\item Once you can accept the universe as matter expanding into nothing that is something, wearing stripes with plaid comes easy.

\item Two things are infinite: the universe and human stupidity; and I'm not sure about the universe.

\end{enumerate}

\vfill

%% Apart from the name and title of the supervisor, the following text is
%% dictated by the promotieregelement.
\begin{center}
These propositions are regarded as opposable and defendable, and have been approved as such by the promotor prof.\ dr.\ A.\ Kleiner.
\end{center}

\end{document}

