\chapter{\LaTeX\ quality assurance}

Before handing your work over to others, there are a few things you can do as a basic quality assurance (QA):
\begin{itemize}
  \item Check your output for missing references (indicated by a double question mark, you may use \verb|pdftotext| to automate this) or look at the blg and log files, where these will be indicated as well
  \item Use a spelling checker
  \begin{itemize}
    \item Overleaf checks your spelling by default.
    \item In \TeX{}studio you can set the spelling check at:\\
      \TeX{}studio Options \(\to\) Configure \TeX{}studio\ldots \(\to\) Language Checking.
    \item You can use Aspell (\url{http://aspell.net/}) to check the spelling in *.tex files from the command line.
    \item If all else fails, you can open a tex file in MS Word and use their spelling and grammar checker
  \end{itemize}
  \item Check consistency of capitalisation in the table of contents
  \item Consistency in bibliography
  \begin{itemize}
    \item Capitalisation of titles
    \item Notation of author names
    \item Abbreviation and spelling of journals
    \item Some Dutch names are capitalized differently depending on wether they are preceded by initials or given names.\footnote{https://onzetaal.nl/taalloket/hoofdletters-namen-nederland}.
      For this, you may use the biblatex command \verb|\autocap|. The same holds for Arabic names, but not, for instance Belgian or German.
  \end{itemize}
  \item Search through your code for words you have likely misspelled (or mix British and American spelling)
  \begin{itemize}
    \item In Windows: \verb"ls -R *.tex | sls 'teh'"
    \item In Linux: \verb|grep -iR 'teh' *.tex|
    \item In Apple: \verb|grep -i 'teh' **/*.tex|
  \end{itemize}
  \item You can also search for regular expressions (regex), e.g.:
  \begin{itemize}
    \item \verb|"\s[\"']\w"| (grep) or \verb|'\s[''"]\w'| (sls): A space, newline, etc. followed by closing single or double quotes, followed by a word character (e.g. a letter). Most likely, these should be replaced by opening quotes (` or ``).
    \item \verb|"\b(\w+) \1\b"| repeated word
    \item \verb|"\b[A-Z][A-Z]+[a-z]"| word starting with two capitals
    \item In your *.bib files:
    \begin{itemize}
      \item \verb|"author\s*=.*\w\.\w"| initial without following space.
      \item \verb|"author\s*=.*\b\w\s\w"| initial without following period.
      \item \verb|"url\s*=.*doi"| DOI given as URL instead of DOI directly
      \item \verb|"doi\s*=.*doi\.org"| DOI including `doi.org'
      \item \verb|"[Uu]rl.*[^\\]#"| Forgot to escape \# in URL
    \end{itemize}
    \item Depending on your citation style:
    \begin{itemize}
      \item space before \verb|cite|
      \item no space before \verb|cite|
      \item parenthesis around \verb|cite|
      \item no parenthesis around \verb|cite|
      \item \ldots
    \end{itemize}
    \item \verb|grep -rnPiR "[^\x09\x0D\x20-\x7E\xBF-\xFF]" *.tex| (or\break\verb|*.bib| `weird' characters (that may look normal) probably caused by copying something from the a pdf file, which might cause \LaTeX\ to error.
    \item When not using 'french spacing': patterns which likely confuse periods indicating an abbreviation with end of sentence and vice versa.
  \end{itemize}
  \item Check your output for missing references (indicated by a double question mark, you may use \verb|pdftotext| to automate this) or look at the log files, where these will be indicated as well
  \item Chk\TeX\ (\url{https://www.ctan.org/pkg/chktex}) is written specifically to search for common errors in *.tex files
  \item All of these suggestions work best when automated, for instance in a Makefile. Doing it by hand is way too boring, so you are very likely to forget running some of these tests on the final version of your thesis.
\end{itemize}
